Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-11-23 psy_peds_3.Rmd
add bootstrap pvalues

files <- readInputFiles( path      = folder_4ce_files, 
                         separator = ",",
                         skip      = 0, 
                         verbose   = FALSE )

@@

pvalue_coeff_interaction <- round(
  (1- max(
    sum(bootstrapped_coefficients_df[["periodduring_pandemic:time"]] > 0,
        bootstrapped_coefficients_df[["periodduring_pandemic:time"]] < 0)
  )/nrow(df)) * 2
  , 3)

>>>>

getwd()
files <- readInputFiles( path      = folder_4ce_files, 
                         separator = ",",
                         skip      = 0, 
                         verbose   = FALSE )

@@

pvalue_coeff_interaction <- round(
  (1- max(
    sum(bootstrapped_coefficients_df[["periodduring_pandemic:time"]] > 0),
        sum(bootstrapped_coefficients_df[["periodduring_pandemic:time"]] < 0)
  )/nrow(bootstrapped_coefficients_df)) * 2
  , 3)
